---
title: "GBC Vignette"
author: "Kahina"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{GBC Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## gbc Vignette
  The gbc package includes an implementation of Graph Based Clustering  Method  (GBC[1][2]) for the R platform. A new method  of  clustering created  by  the respective  both  IT professors Fabrice MUHLENBACH [3] and Stéphane LALLICH [4]. This vignette introduces how to interface with GBC features.
  
To understand how GBC works, we refer to the Rmarkdown documentation a good  resource for documentation used to goes over the basic concepts of the GBC algorithm. For the sake of simplicity, consider the same sample dataset : (RUSPINI).


```{r}
library(gbc)
plot(ruspini)
```

## Examples 

## Results and figures

## References
1. article_FM_SL_ICDM_2009 - Fabrice MUHLENBACH [1] & Stéphane LALLICH [2], « A New Clustering Algorithm Based on Regions of Influence with Self-Detection of the Best Number of Clusters », International Conference of Data Mining (ICDM), année 2009, pages 1-6.

2. EGC2009_FM_6_pages - Fabrice MUHLENBACH [1], « Méthode de regroupement par graphe de voisinage », Extraction et gestion des connaissances (EGC'2009), Jan 2009, Strasbourg, France (https://hal.archives-ouvertes.fr/hal-00364651v2), année 2009, pages 1-6.

3. Fabrice MUHLENBACH, Maître de Conférences en Informatique et Enseignant Chercheur au laboratoire Hubert Curien, UMR CNRS 5516, à L’Université Jean Monnet de Saint-Étienne, France, (https://perso.univ-st-etienne.fr/muhlfabr).

4. Stéphane LALLICH, Professeur émérite à l'Université Lyon 2, Enseignant Chercheur au laboratoire laboratoire ERIC (EA 3083), à L’Université Lumière Lyon 2, France, (http://eric.univ-lyon2.fr/~lallich).

